---
title: "iGraphNetwork"
author: "Kevin.obrien"
date: "March 3, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```


Network Analysis and Visualization with R and igraph


## Networks in igraph
```{r}
rm(list = ls()) # Remove all the objects we created so far.

library(igraph) # Load the igraph package
```

## Create networks
The code below generates an undirected graph with three edges. The numbers are interpreted as vertex IDs, so the edges are 1->2, 2->3, 3->1.
```{r graph1a }
g1 <- graph( edges=c(1,2, 2,3, 3, 1), n=3, directed=F ) 

plot(g1) # A simple plot of the network - we'll talk more about plots later
```
## Graph 1 (Contd)
```{r graph1b}
class(g1)
## [1] "igraph"
g1
## IGRAPH U--- 3 3 -- 

## + edges:

## [1] 1--2 2--3 1--3
# Now with 10 vertices, and directed by default:
```


## Graph 2

```{r}
g2 <- graph( edges=c(1,2, 2,3, 3, 1), n=10 )

plot(g2)   

```

## Graph 2 (contd)
```{r}
g2
## IGRAPH D--- 10 3 -- 

## + edges:

## [1] 1->2 2->3 3->1
```

## Graph 3
```{r}
g3 <- graph( c("Alice", "Barry", "Barry", "Ciara", "Ciara", "Alice")) # named vertices

# When the edge list has vertex names, the number of nodes is not needed

plot(g3)
```



##
```{r}
g3
## IGRAPH DN-- 3 3 -- 

## + attr: name (v/c)

## + edges (vertex names):

## [1] Alice->Barry  Barry ->Ciara Ciara->Alice

```

## Graph 4

```{r}
g4 <- graph( c("Alice", "Barry", "Barry", "Jack", "Barry", "Jack", "Alice", "Alice"), 

             isolates=c("Dermot", "Janis", "Jennifer", "Justin") )  

# In named graphs we can specify isolates by providing a list of their names.
```
##

```{r}
plot(g4, edge.arrow.size=.5, vertex.color="gold", vertex.size=15, 

     vertex.frame.color="gray", vertex.label.color="black", 

     vertex.label.cex=0.8, vertex.label.dist=2, edge.curved=0.2) 
```